Generalized spaces for constructive algebra

### 2020-04-08 paper-herrsching2019/main.tex
Heine­Borel for uncountable covers

\begin{exercise}{Spatiality of the localic reals}%
\label{ex:spatiality-reals}%
\newcommand{\fa}{\ensuremath{(\!\cdot}}%
\newcommand{\fb}{\ensuremath{\cdot\!)}}%
Let~$\RR$ be the localic real line, defined as the classifying locale of the
theory~$\TT$ of Dedekind cuts as as introduced on
page~\pageref{par:dedekind-cuts}. For rational numbers~$x,y$, let~``$\fa x,y
\fb$'' denote the formula~$\alpha_x \wedge \beta_y$. Let~$(x,y)$ denote the
open interval~$\{ \xi \in \Pt(\RR) \,|\, x < \xi < y \}$ in the set of Dedekind reals.
\begin{alphlist}[(f)]
\item Extend the notation to allow for~$x,y=\pm\infty$.
\item Show that the canonical topology on~$\Pt(\RR)$, defined in
Exercise~\ref{ex:canonical-topology}, coincides with the usual Euclidean
topology.
\item Show that any open of~$\RR$ can be written in the form~$\bigvee_i
[\fa x_i,y_i \fb]$ with~$x_i,y_i \in \QQ \cup \{\pm\infty\}$.
\item Let rational numbers be given such that~$(x,y) \subseteq \bigcup_i
(x_i,y_i)$ in~$\Pt(\RR)$. Assume that this open covering has a Lebesgue number.
Show that~$\TT$ proves~$\fa x,y \fb \vdash \bigvee_i \fa x_i,y_i \fb$.
\item Assume that closed intervals in the set of Dedekind reals are
(Heine--Borel) compact. Then redo part~(d), but without the assumption on the
existence of a Lebesgue number.
\item Under the same assumption as in part~(e), show that the localic real line
is spatial.
\end{alphlist}
{\scriptsize\emph{Note.} Exercise~\ref{ex:exotic-locales} lists settings in
which the assumption in part~(e) is not satisfied.\par}
\end{exercise}

>>>>

\begin{exercise}{Spatiality of the localic reals}%
\label{ex:spatiality-reals}%
\newcommand{\fa}{\ensuremath{(\!\cdot}}%
\newcommand{\fb}{\ensuremath{\cdot\!)}}%
Let~$\RR$ be the localic real line, defined as the classifying locale of the
theory~$\TT$ of Dedekind cuts as as introduced on
page~\pageref{par:dedekind-cuts}. For rational numbers~$x,y$, let~``$\fa x,y
\fb$'' denote the formula~$\alpha_x \wedge \beta_y$. Let~$(x,y)$ denote the
open interval~$\{ \xi \in \Pt(\RR) \,|\, x < \xi < y \}$ in the set of Dedekind reals.
\begin{alphlist}[(f)]
\item Extend the notation to allow for~$x,y=\pm\infty$.
\item Show that the canonical topology on~$\Pt(\RR)$, defined in
Exercise~\ref{ex:canonical-topology}, coincides with the usual Euclidean
topology.
\item Show that any open of~$\RR$ can be written in the form~$\bigvee_i
[\fa x_i,y_i \fb]$ with~$x_i,y_i \in \QQ \cup \{\pm\infty\}$.
\item Let rational numbers be given such that~$(x,y) \subseteq \bigcup_i
(x_i,y_i)$ in~$\Pt(\RR)$. Assume that this open covering has a Lebesgue number.
Show that~$\TT$ proves~$\fa x,y \fb \vdash \bigvee_i \fa x_i,y_i \fb$.
\item Assume that closed intervals in the set of Dedekind reals are
(Heine--Borel) compact. Then redo part~(d), but without the assumption on the
existence of a Lebesgue number.
\item Under the same assumption as in part~(e), show that the localic real line
is spatial.
\end{alphlist}
{\scriptsize\emph{Note.} Exercise~\ref{ex:exotic-locales} lists settings in
which the assumption in part~(e) is not satisfied. The converse in part~(f)
also holds. Incidentally, the spatiality of the localic real line is an example
for a statement which requires the full version of the Heine--Borel property,
not only Heine--Borel for countable covers as it is often studied in reverse
mathematics~\cite{normann-sanders:uncountable}.\par}
\end{exercise}
